\newcommand{\ketbb}{\ket{\smash{b^\bot}}}
\newcommand{\tpO}{\smash{\widetilde{\smash{\psi}}^0}}
\newcommand{\ktpO}
{\ket{\tpO}}
\newcommand{\tpI}{\smash{\widetilde{\smash{\psi}}^1}}
\newcommand{\ktpI}
{\ket{\tpI}}
\newcommand{\tfO}{\smash{\widetilde{\phi}^0}}
\newcommand{\ktfO}
{\ket{\tfO}}
\newcommand{\tfI}{\smash{\widetilde{\phi}^1}}
\newcommand{\ktfI}
{\ket{\tfI}}
\newcommand{\psip}{\smash{\psi'}}
\newcommand{\phip}{\smash{\phi'}}
\newcommand{\tarp}{\smash{\overline{\tar}}}
\newcommand{\labp}{\smash{\overline{\lab}}}
\newcommand{\tarz}{\smash{\tar^{0}}}
\newcommand{\taro}{\smash{\tar^{1}}}
\newcommand{\labz}{\smash{\lab^{0}}}
\newcommand{\labo}{\smash{\lab^{1}}}

\section{Access Model} %and Computational Efficiency}
Our proof relied on \Cref{cor:perpy} to give us a basis. This is a pretty arbitrary and maybe computationally powerful black box, so let's try to reduce it to something a little more reasonable. The following is our reduced black box.

\begin{definition}\label{def:access model}
We consider an oracle for $\ket{\psi}$. It takes as input any product operator $\Pi=\bigotimes_{i \in [n]} \Pi_i$ where each $\Pi_i$ is a single-qubit projection operator. It outputs the value $\bra{\psi} \Pi \ket{\psi}$. Note that $\Pi_k=\Id$ is allowed.
\end{definition}
Huang et al.~\cite{huang2024certifying} used the same oracle, but only allowed $\Pi$ to be projectors for computational basis strings. It is useful to observe, for example, that if we had a description of $\ket{\tar}$ as a matrix product state of small bond dimension, we could efficiently emulate the oracle.

Now, we will show that this access model allows us to adaptively compute a DT basis as in \Cref{cor:perpy} and implement the corresponding measurements efficiently.


\begin{lemma}\label{lem:computational efficiency}
    Given access to $\ket{\smash{\psi^{ 0}}}$ and $\ket{\smash{\psi^{ 1}}}$ via this model, we can implement measuring in the DT basis defined in \Cref{cor:perpy} (making $\ket{\smash{\psi^0}}$ and $\ket{\smash{\psi^1}}$ phase states), using $O(n)$ time and single-qubit measurements.
\end{lemma}
\begin{proof}
  For $t=0$, initialize $\ket{\smash{\psi^0_t}}=\ket{\smash{\psi^0}}$, $\ket{\smash{\psi^1_t}}=\ket{\smash{\psi^1}}$, and the trivial operator $\Pi_t=1$.

  Looping over $t<n$, we want to compute the reduced states $\rho^0_t = \Tr_{[n]\setminus \{t+1\}}(\ketbra{\smash{\psi^0_t}}{\smash{\psi^0_t}})$ and $\rho^1_t = \Tr_{[n]\setminus \{t+1\}}(\ketbra{\smash{\psi^1_t}}{\smash{\psi^1_t}})$. The oracle helps us do this as follows: For $a\in\{0,+,\mathfrak{i}\}$, build the measurement operator
\[
  \Pi = \Pi_t \otimes \ketbra{b}{b} \otimes \Id^{\otimes (n - t - 1)}
\]
  Then measure $\bra{\smash{\psi^0}}\Pi\ket{\smash{\psi^0}}\text{ and }\bra{\smash{\psi^1}}\Pi\ket{\smash{\psi^1}}$. Since we get real values back, we can exactly reconstruct $\rho^0_t$ from these three values.

  Note that this single-qubit state reconstruction would be more difficult without the oracle. Without this oracle we would replace $\bra{a} \ket{a}$ with $\bra{b} \ket{b}$ for both $b \in \{a, a^{\bot}\}$. We would repeat this $N$ times to estimate $\langle \rho_t^0 \mid a\rangle$ with an error of $\frac 1 {\sqrt N}$. Finally, we would project back onto the Bloch ball.
    
    As in \Cref{cor:perpy}, let $\ket{e_t}$ be perpendicular to both $\rho^0_t$ and $\rho^1_t$ on the Bloch sphere and measure the $(t+1)$th qubit in the basis $\ket{e_t},\ket{\smash{e_t^\perp}}$. Then set $\Pi_{t+1}=\Pi_t \otimes\ketbra{b}{b}$, where $\ket{b}\in \{\ket{e_t},\ket{\smash{e^\perp_t}}\}$ was the outcome of this measurement. Then $\ket{\smash{\psi^0_{t+1}}}\propto\Pi_{t+1}\ket{\smash{\psi^0}}$ and $\ket{\smash{\psi^1_{t+1}}}\propto\Pi_{t+1}\ket{\smash{\psi^1}}$ and we increase $t$ by $1$.

    Repeating for all $t$ gives a measurement outcome in a DT basis satisfying the conclusion of \Cref{cor:perpy}. Computing the $t^{th}$ measurement and updating the query take $O(1)$ time, so the overall runtime is $O(n)$.

\end{proof}
Given \Cref{lem:computational efficiency}, we see that \Cref{alg:main} can be implemented in time $O(n)$ under the access model of \Cref{def:access model}. For measurement in the decision tree basis $\calT_x$ (where $x$ is the outcome of measuring the first $k-1$ qubits), we use \Cref{lem:computational efficiency} with $\ket{\psi^0}=\ket{\tar^{x0}}$ and $\ket{\psi^1}=\ket{\tar^{x1}}$.
