\section{Introduction}\label{sec:intro}
Quantum state certification asks whether a state prepared in the lab is close to a known target. In this report the target is a pure $n$-qubit state $\ket{\psi_{target}}$, given by a classical description, while the lab provides copies of an unknown state $\rho_{lab}$. The natural score is the fidelity
\[
    \bra{\psi_{target}}\rho_{lab}\ket{\psi_{target}}
\]
which is $1$ exactly when the lab state is the target state.

If arbitrary measurements were available, we could just apply the POVM operation
\[
    \{\ket{\psi_{target}}\bra{\psi_{target}}, \Id-\ket{\psi_{target}}\bra{\psi_{target}}\}
\]
This succeeds with the best possible probability, and if we want to improve we can repeat on additional copies. The difficulty is that this measurement is itself an $n$-qubit operation tailored to $\ket{\psi_{target}}$. For a highly entangled target, that might make sense if we had a trustworthy machine and were calibrating a new machine. But in general implementing this is just as hard as preparing the target state in the first place.

The main result of Gupta, He, and O'Donnell~\cite{gupta2025few} is that this global target-dependent measurement can be replaced by adaptive single-qubit measurements:

\begin{theorem}\label{thm:main}
    There exists an algorithm that takes a classical description of an $n$-qubit pure state $\ket{\psi_{target}}$ and a single copy of an $n$-qubit (possibly mixed) state $\rho_{lab}$, performs only single-qubit measurements on $\rho_{lab}$, and outputs:
    \begin{itemize}
        \item \textsc{Accept} with probability at least $\mathrm{Fid} \coloneqq \bra{\psi_{target}}\rho_{lab}\ket{\psi_{target}}$
        \item \textsc{Reject} with probability at least $\mathrm{Infid}/n \coloneqq (1-\mathrm{Fid})/n$
    \end{itemize}
\end{theorem}

The setting is motivated by cases where a useful quantum state has a well understood classical representation but may be hard to prepare or inspect directly. For example, neural quantum states give compact variational descriptions of many-body wavefunctions~\cite{carleo2017solving}. Tensor-network states such as matrix product states give another structured representation for physically important systems~\cite{verstraete2006matrix}. In both cases, one may have efficient classical access to amplitudes or marginal probabilities of the target state while still wanting a certification procedure that uses only simple measurements on the lab system.

\subsection{Tomography (density estimation)}
Before discussing state certification, we start with the baseline problem of \emph{tomography}. Here the goal is to produce a full classical estimate $\wh{\rho}$ of an unknown density matrix $\rho \in \C^{d \times d}$, given $n$ copies $\rho^{\otimes n}$, up to error~$\eps$ (whp) for some notion of ``distance''. A basic strategy is to measure an informationally complete family of observables on many copies, estimate their expectation values, and then reconstruct a density matrix consistent with those estimates. We use $k$ to denote the \emph{rank} of $\rho$, which is $1$ when $\rho$ is a pure state, and in general is at most~$d$. The number of copies needed depends strongly on both $k$ and the distance measure (see \Cref{sec:distances} for a review).

In practice, tomography turns measurement outcomes into estimates of the coordinates of~$\rho$. For example, one can measure Pauli observables on many independently prepared copies, estimate each expectation value from its empirical average, and expand the density matrix in the Pauli basis using those estimates. Since the reconstructed matrix may not be positive semidefinite or have trace~$1$, practical algorithms usually add a projection or maximum-likelihood step to return a valid density matrix.

Here is how many copies are needed for tomography under different distance measures:

\begin{table}[H]
\centering
\small
\begin{tabular}{p{0.16\linewidth}p{0.26\linewidth}p{0.20\linewidth}p{0.28\linewidth}}
\toprule
Reference & Setting & Copies \\
\midrule
\cite{haah2016sample} & Infidelity & $O(kd/\epsilon)\log(d/\epsilon)$ \\
  \cite{haah2016sample} & Trace distance & $O(kd/\epsilon^2)\log(d/\epsilon)$ \\
\cite{swan1swan2_2016efficient} & Hilbert--Schmidt distance & $O(d/\eps^2)$ \\
\cite{swan1swan2_2016efficient} & Trace distance & $O(kd/\epsilon^2)$ \\
\cite{swan1swan2_2016efficient} & Rank-$k$ approximator & $O(kd/\epsilon^2)$ \\
\cite{swan1swan2_2017efficient} & Infidelity & $O(k^2d/\epsilon)$ \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Density testing}

Tomography results face the inherent issue that $n = \wt{\Theta}(d^2)$ copies are needed in the general case for most distance metrics, and this is exponential in the number of qubits $n$. Property testing asks for less information: instead of learning $\rho$, it asks for a decision about $\rho$. This shift can reduce the sample complexity from learning a full object to estimating one property. Montanaro and de~Wolf~\cite{montanaro2013survey} survey this viewpoint for quantum states.

A typical quantum property testing problem involves two disjoint classes $\calC_1$, $\calC_2$ of $d$-dimensional quantum states. Given $n$ copies of an unknown $\rho$, promised to be in either~$\calC_1$ or~$\calC_2$, the task is to distinguish which is the case (whp) using few copies of~$\rho$. In particular, the \emph{quantum state certification} problem for fixed state $\sigma \in \C^{d \times d}$ is the case when $\calC_1 = \{\sigma\}$ and $\calC_2 = \{ \rho : \mathrm{D}(\rho,\sigma) > \eps\}$ for some notion $\mathrm{D}(\cdot, \cdot)$ of distance and some parameter~$\eps$.

Here is how many copies are needed for tomography under different distance measures:
When $\sigma$ is a \emph{pure} state and arbitrary measurements are allowed, certification is much cheaper than tomography. Mixed targets are less well understood. See the table below for a summary of results.

\begin{table}[H]
\centering
\small
\begin{tabular}{lll}
\toprule
Reference & Setting & Copies \\
\midrule
\cite{montanaro2013survey} & Pure target $\sigma$, infidelity & $O(1/\eps)$ \\
\cite{montanaro2013survey} & Pure $\sigma$, trace-distance & $O(1/\eps^2)$ \\
%\cite{montanaro2013survey} & Unknown pure $\sigma$ and lab states, infidelity & O(1/\eps)\\
\cite{flammia2011direct,da2011practical,aolita2015reliable} & Pure $\sigma$, Pauli observables, fidelity & $O(d/\eps^2)$ \\
\cite{odonnell2015quantum} & $\sigma = \Id/d$, fidelity & $\Theta(d/\eps^2)$ \\
  \cite{odonnell2015quantum} & Purity $\tr(\rho^2)$ & $O(d/\eps)$ \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Restricted measurements} \label{sec:restricted-measurement}

The copy-efficient protocols above hide a second resource: measurement complexity. They implicitly assume one can implement either the two-outcome POVM $\{\ket{\psi_{target}}\bra{\psi_{target}}, \Id - \ket{\psi_{target}}\bra{\psi_{target}}\}$ or a SWAP test~\cite{buhrman2001quantum} between $\rho_{lab}$ and a freshly prepared copy of $\ket{\psi_{target}}$. Both use few copies, but both require preparing or recognizing $\ket{\psi_{target}}$, which may be a highly entangled $n$-qubit pure state. Therefore, a number of techniques and papers have sprung up bounding copy-efficiency using restrited measurements.  The main result~\cite{gupta2025few} that we present here falls into this category.

The framework of \emph{classical shadows}~\cite{huang2020predicting} partially side-steps this circularity. It replaces target-dependent measurements with random Clifford measurements on independent copies of $\rho$, producing classical data from which many observables can later be estimated.

A Clifford unitary is a quantum operation that maps Pauli operators to Pauli operators under conjugation. If $U$ is Clifford and $P$ is Pauli, then $UPU^\dagger$ is also Pauli, up to a sign or phase. Standard examples include Hadamard, phase, and CNOT gates. Clifford circuits can create entanglement and nontrivial stabilizer states, but they remain classically tractable through the stabilizer formalism. In a random Clifford measurement, one samples such a unitary, applies it to the state, measures in the computational basis, and records both the unitary and the outcome.

Applied to the observable $\ket{\psi_{target}}\bra{\psi_{target}}$, this gives an estimate of $\Fid{\rho}{\ket{\psi_{target}}\bra{\psi_{target}}}$ to additive error~$\eps$ using $O(1/\eps^2)$ copies, independent of dimension. The tradeoff is that random Clifford measurements require deep circuits, and the classical post-processing depends on computing overlaps between $\ket{\psi_{target}}$ and random stabilizer states.

If the measurements must be single-qubit Pauli measurements, the closest prior protocols are direct fidelity estimation~\cite{flammia2011direct} and a Pauli-based variant of classical shadows~\cite{huang2020predicting}. These methods simplify the measurements, but they shift the burden back to sample complexity in the worst case: direct fidelity estimation depends on the system dimension $d = 2^n$, while Pauli shadows depend on the weight of the observable being estimated. Pauli shadows are therefore well suited to certifying small subsystems, but not to estimating fidelity with an arbitrary highly entangled $n$-qubit target.

\begin{table}[H]
\centering
\small
\begin{tabular}{lll}
\toprule
Reference & Setting & Copies \\
\midrule
\cite{buhrman2001quantum} & SWAP test with target copies & copy-efficient \\
\cite{huang2020predicting} & Random Clifford shadows, fidelity & $O(1/\eps^2)$ \\
\cite{flammia2011direct} & Pauli observables, fidelity & $O(d/\eps^2)$ \\
\cite{huang2020predicting} & Single-qubit Pauli shadows & observable-dependent \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Structured state classes} \label{sec:structured-classes}

For target states drawn from structured classes, simple measurements can certify much more than they can for arbitrary targets. The common theme is that the target's structure makes the relevant fidelity information visible through a smaller family of observables. Stabilizer states and outputs of shallow quantum circuits admit efficient certification by direct fidelity estimation~\cite{flammia2011direct} or by randomized Pauli shadows~\cite{huang2020predicting}. Similar structure supports protocols for hypergraph states and output states of IQP circuits~\cite{takeuchi2018verification}, bosonic Gaussian states~\cite{aolita2015reliable}, and fermionic Gaussian states~\cite{gluza2018fidelity}. For generic random target states, cross-entropy benchmarking (XEB) estimates a related fidelity quantity under suitable noise models~\cite{arute2019quantum}.

A complementary line of work asks how the answer changes when the target may be mixed or when we allow a different measurement model~\cite{buadescu2019quantum}.

\subsection{The asymptotic regime} \label{sec:asympt-state-discrim}

There is also a related asymptotic theory of state discrimination. In the simplest version, two states $\sigma_1,\sigma_2 \in \C^{d \times d}$ are known, and one receives copies of either $\sigma_1$ or $\sigma_2$. The non-asymptotic question asks for the least number of copies~$n$ needed to distinguish the two cases with high probability --- say, with both type~I and type~II errors at most $\delta=1/3$. One can reduce this~$\delta$ to any smaller constant by increasing~$n$ by a constant factor.

By contrast, quantum hypothesis testing studies the asymptotic regime $n \to \infty$ and asks how quickly the optimal error rate decays. One seeks the best constant~$R$ such that, given $n$ copies, the error probabilities can be bounded by $(R+o(1))^n$. Such results identify the right exponent, but they do not directly say how large $n$ must be before the asymptotic expression becomes accurate; this threshold can depend on dimension or spectral parameters of $\sigma_1$ and $\sigma_2$.

A good survey of the results in the asymptotic regime appears in~\cite{audenaert2008asymptotic}; they review known quantum versions of Stein's Lemma and Sanov's Theorem, and prove quantum versions of Chernoff's Bound and the the Hoeffding--Blahut--Csisz\'{a}r--Longo bound. For example, in the basic hypothesis testing problem described above, they prove that the best rate~$R$ is given by $Q_{\text{min}}\diverg{\sigma_1}{\sigma_2} = \min_{0 \leq s \leq 1}\tr(\sigma_1^s \sigma_2^{1-s})$ (a quantity that is within a factor of~$2$ of the infidelity between $\sigma_1$ and~$\sigma_2$).
