\IfFileExists{../diagrams/huang_templates.tex}{\input{../diagrams/huang_templates.tex}}{\input{diagrams/huang_templates.tex}}

\section{Introduction}

\begin{frame}{Tomography}
    \begin{columns}[T,onlytextwidth]
        \begin{column}{0.56\textwidth}
            \begin{itemize}
                \item<1-> Tomography estimates the full density matrix $\rho \in \mathbb{C}^{d\times d}$
                \item<1-> Number of copies is polynomial in $d$
                \item<2-> With $d=2^n$, this is exponential in the number of qubits.
            \end{itemize}

            \vspace{0.6em}
            \uncover<3->{
                We only need to distinguish high fidelity from low fidelity with one fixed target state, not reconstruct $\rho_{\text{lab}}$
            }
        \end{column}
        \begin{column}{0.38\textwidth}
            \centering
            \begin{tikzpicture}[font=\small, >=Stealth]
                \node[draw, rounded corners=3pt, minimum width=2.25cm, minimum height=0.8cm, fill=blue!8] (copies) at (0,1.2) {$\rho^{\otimes m}$};
                \node[draw, rounded corners=3pt, minimum width=2.25cm, minimum height=0.8cm, fill=orange!12] (tomo) at (0,0) {Tomography};
                \node[draw, rounded corners=3pt, minimum width=2.25cm, minimum height=0.8cm, fill=green!10] (est) at (0,-1.2) {$\widehat{\rho}$};
                \draw[->, thick] (copies) -- (tomo);
                \draw[->, thick] (tomo) -- (est);
                \uncover<2->{\node[align=center, text=red!70!black] at (0,-2.1) {$m$ scales with\\$d=2^n$};}
                \HuangUseBoundingBox{-1.35}{-2.45}{1.35}{1.65}
            \end{tikzpicture}
        \end{column}
    \end{columns}
\end{frame}

\begin{frame}{State Certification}
    \begin{center}
        \resizebox{0.78\textwidth}{!}{\input{../diagrams/huang_state_certification.tex}}
    \end{center}

    \vspace{-0.3em}
    \begin{block}{Goal}
        Given a classical description of a target pure state $\ket{\psi_{\text{target}}}$ and one copy of an unknown lab state $\rho_{\text{lab}}$, decide whether
        \[
            \mathrm{Fid}=\bra{\psi_{\text{target}}}\rho_{\text{lab}}\ket{\psi_{\text{target}}}
        \]
        is large, using only simple measurements on $\rho_{\text{lab}}$.
    \end{block}
\end{frame}

\begin{frame}{Naive Certification}
    \begin{columns}[T,onlytextwidth]
        \begin{column}{0.5\textwidth}
            It's trivial! Just use
            \[
                \left\{\ket{\psi_{\text{target}}}\!\bra{\psi_{\text{target}}},
                I-\ket{\psi_{\text{target}}}\!\bra{\psi_{\text{target}}}\right\}.
            \]

            \pause
            \vspace{0.5em}
            Equivalently, one may use a SWAP test against a freshly prepared copy of $\ket{\psi_{\text{target}}}$.
    \pause

    \vspace{0.3em}
      Circular: We need $\ket{\psi_{\text{target}}}$ to test $\ket{\psi_{\text{target}}}$
        \end{column}
        \begin{column}{0.46\textwidth}
            \centering
            \resizebox{\linewidth}{!}{\input{../diagrams/huang_previous_deep_circuit.tex}}
        \end{column}
    \end{columns}

\end{frame}

\begin{frame}{Classical Shadows}
    \begin{columns}[T,onlytextwidth]
        \begin{column}{0.48\textwidth}
            \begin{center}
                \makebox[0pt][c]{\hspace*{-2.5cm}\resizebox{0.95\linewidth}{!}{\input{../diagrams/huang_random_clifford.tex}}}
            \end{center}

            \vspace{0.4em}
            \begin{block}{Random Clifford shadows}
                Number of samples fixed wrt dimension

                Deep circuits and exponential classical postprocessing
            \end{block}
        \end{column}
        \begin{column}<2->{0.48\textwidth}
            \begin{center}
                \makebox[0pt][c]{\hspace*{-2.5cm}\resizebox{0.95\linewidth}{!}{\input{../diagrams/huang_random_pauli.tex}}}
            \end{center}

            \vspace{0.4em}
            \begin{block}{Single-qubit Pauli shadows}
                Number of samples grows exponentially

                Simple to build
            \end{block}
        \end{column}
    \end{columns}
\end{frame}

\begin{frame}{Restricted Measurements}
    \begin{itemize}
        \item Direct fidelity estimation and Pauli-shadow variants work well for structured observables and target families.
        \item Efficient certification is known for stabilizer states, shallow-circuit outputs, hypergraph states, IQP outputs, and Gaussian states.
        \item For generic random targets, XEB can work under suitable noise assumptions, but it is not a general certification guarantee.
    \end{itemize}

    \vspace{0.4em}
    \begin{center}
        \resizebox{0.58\textwidth}{!}{\input{../diagrams/huang_xeb_z_basis.tex}}
    \end{center}
\end{frame}

\begin{frame}{Main Theorem}
    \begin{theorem}
      There exists a certification algorithm that takes a classical description of an $n$-qubit {\bf pure} state $\ket{\psi_{\text{target}}}$ and a single copy of an $n$-qubit {\bf mixed} state $\rho_{\text{lab}}$, performs only {\bf single-qubit measurements}, and outputs:
        \begin{itemize}
            \item \textsc{Accept} with probability at least
            $\mathrm{Fid} := \bra{\psi_{\text{target}}}\rho_{\text{lab}}\ket{\psi_{\text{target}}}$
            \item \textsc{Reject} with probability at least
            $\mathrm{Infid}/n := (1-\mathrm{Fid})/n$
        \end{itemize}
    \end{theorem}

    \pause
    To get an arbitrarily high success rate $1 - \epsilon$, just repeat $\frac n {\mathrm{Infid}} \log(1/\epsilon)$ times.
    %\begin{center}
    %    One qubit at a time: compare locally, guarantee globally.
    %\end{center}
\end{frame}

\begin{frame}{Motivating Applications}
    \begin{center}
        \resizebox{0.86\textwidth}{!}{\input{../diagrams/huang_applications_overview.tex}}
    \end{center}

    \begin{itemize}
        \item Benchmark a noisy quantum device against its intended output.
        \item Train or certify neural quantum-state models using fidelity as the objective.
        \item Optimize parametrized circuits toward a target state without implementing the target projector.
    \end{itemize}
\end{frame}

\begin{frame}{What We Need From the Protocol}
    \begin{columns}[T,onlytextwidth]
        \begin{column}{0.5\textwidth}
            \begin{enumerate}
                \item Single-qubit measurements
                \item Only use classical description of target
            \end{enumerate}
        \end{column}
        \begin{column}{0.46\textwidth}
            \centering
            \resizebox{\linewidth}{!}{\input{../diagrams/huang_shadow_naive.tex}}
        \end{column}
    \end{columns}

    \vspace{0.4em}
    \begin{center}
        The algorithm resolves the ``locally maximally mixed'' obstacle by conditioning on previous measurement outcomes.
    \end{center}
\end{frame}
